Learning Multiple Networks via Supervised Tensor Decomposition

### 2020-11-15 tensor_regress/NeurIPSw/camera_ready/neuripsw_tensor_c_v3.tex
v3

{\bf Notation.} We follow the tensor notation as in~\cite{kolda2009tensor}. The multilinear multiplication of a tensor $\tY\in\mathbb{R}^{d_1\times \cdots\times d_K}$ by matrices $\mX_k=\entry{x_{i_k,j_k}^{(k)}}\in\mathbb{R}^{p_k\times d_k}$ is defined as $\tY\times\{\mX_1,\ldots,\mX_K\} =\entry{\sum_{i_1,\ldots,i_K}y_{i_1,\ldots,i_K}x_{j_1,i_1}^{(1)}\cdots x_{j_K,i_K}^{(K)}}$,
which results in an order-$K$ $(p_1,\ldots,p_K)$-dimensional tensor. The inner product between two tensors of equal size is defined as $\langle \tY,\ \tY'\rangle =\sum_{i_1,\ldots,i_K}y_{i_1,\ldots,i_K}y'_{i_1,\ldots,i_K}$. We use $\FnormSize{}{\cdot}$, $\mnormSize{}{\cdot}$, and $\text{vec}(\cdot)$ to denote tensor F-norm, tensor infinity norm, and the operation that reshapes the tensor into a vector, respectively. We also use $\onorm{\cdot}_{\sigma}$ and $\otimes$ to denote the matrix spectral norm and Kronecker product of matrices, respectively. For ease of notation, we allow basic arithmetic operators (e.g.,\ $+, -$) and univariate functions $f\colon \mathbb{R}\to \mathbb{R}$ to be applied to tensors in an element-wise manner.

>>>>

{\bf Notation.} We follow the tensor notation as in~\cite{kolda2009tensor}. The multilinear multiplication of a tensor $\tY\in\mathbb{R}^{d_1\times \cdots\times d_K}$ by matrices $\mX_k=\entry{x_{i_k,j_k}^{(k)}}\in\mathbb{R}^{p_k\times d_k}$ is defined as $\tY\times\{\mX_1,\ldots,\mX_K\} =\entry{\sum_{i_1,\ldots,i_K}y_{i_1,\ldots,i_K}x_{j_1,i_1}^{(1)}\cdots x_{j_K,i_K}^{(K)}}$,
which results in an order-$K$ $(p_1,\ldots,p_K)$-dimensional tensor. The inner product between two tensors of equal size is defined as $\langle \tY,\ \tY'\rangle =\sum_{i_1,\ldots,i_K}y_{i_1,\ldots,i_K}y'_{i_1,\ldots,i_K}$. We use $\FnormSize{}{\cdot}$ and $\mnormSize{}{\cdot}$ to denote tensor F-norm and tensor infinity norm, respectively. We use $\textup{vec}(\cdot)$ to denote the operation that reshapes the tensor into a vector, and $\text{Unfold}_k(\cdot)$ to denote the operation that reshapes the tensor along mode $k$ into a matrix of size $d_k$-by-$\prod_{i\neq k}d_i$.  We also use $\onorm{\cdot}_{\sigma}$ and $\otimes$ to denote the matrix spectral norm and Kronecker product of matrices, respectively. For ease of notation, we allow basic arithmetic operators (e.g.,\ $+, -$) and univariate functions $f\colon \mathbb{R}\to \mathbb{R}$ to be applied to tensors in an element-wise manner.
